---
title: "Data Dictionary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Dictionary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Most tables are derived from the MEDLINE XML files, parsed according to the [MEDLINE®PubMed® XML Element Descriptions and their Attributes](https://www.nlm.nih.gov/bsd/licensee/elements_descriptions.html). The `source` column indicates the corresponding element in the MEDLINE XML. All elements other than those for the pmid_status table and the citation table are nested within the PubmedArticle element. "attr" indicates a named attribute in the XML, and "int position" indicates an integer to index each item in a list. The citation table is derived from the [NIH Open Citation Collection](https://nih.figshare.com/collections/iCite_Database_Snapshots_NIH_Open_Citation_Collection_/4586573).

```{r, echo = FALSE}
dd = data.table::fread(system.file('extdata', 'data_dictionary.csv', package = 'pmparser'))
knitr::kable(dd)
```
